Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/advup.tex

\subsection{Advantage Updating}
\label{subsec:reparam}
To define an object which contains the same information on actions as
$Q^\pi_\deltat$, but admits an action dependant continuous time limit, it is
natural to define
\begin{align}
	A^\pi_\deltat(s, a) &\mathdef \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat},
    \label{eq:adv}
\end{align}
a rescaled version of the advantage function \cite{adv_upd}, as the difference between between
$Q^\pi_\deltat(s, a)$ and $V^\pi\deltat(s)$ is of order $\bigO(\deltat)$.
Contrary to the action state value function, the rescaled advantage function converges when $\deltat$ goes to $0$
to an action dependent quantity which contains the necessary information for policy improvement:

>>>>

\subsection{Advantage Updating}
\label{subsec:reparam}
To define an object which contains the same information on actions as
$Q^\pi_\deltat$, but admits an action dependant continuous time limit, it is
natural to define \cite{adv_upd}
\begin{align}
	A^\pi_\deltat(s, a) &\mathdef \frac{Q^\pi_\deltat(s,a) - V^\pi_\deltat(s)}{\deltat},
    \label{eq:adv}
\end{align}
a rescaled version of the advantage function \cite{adv_upd}, as the difference between between
$Q^\pi_\deltat(s, a)$ and $V^\pi\deltat(s)$ is of order $\bigO(\deltat)$.
Contrary to the action state value function, the rescaled advantage function converges when $\deltat$ goes to $0$
to an action dependent quantity which contains the necessary information for policy improvement:
